---
title: 'All python imports: Terms classified into live and products'
output:
  word_document: default
  html_document: default
date: "2023-03-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
The aim is to plot bar plots for data on all imports. The total imports (global) have been categorized into live (CITES database: Term = "live" and "eggs (live)") or products (CITES database: everything besides those included in "live")


##List of species
```{r}
library(vkmCites)
library(ggplot2)
library(tidyverse)
unique(vkmCites::Pythons$Taxon)
```
#List of "Terms"
What to do with the meaningless products - frog legs or ivory carvings for example.
```{r}
unique(vkmCites::Pythons$Term)
```



##Plots
```{r}
library(viridis)
Plot_imports(data = vkmCites::Pythons, Species = "Apodora papuana", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Aspidites melanocephalus", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Liasis mackloti", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Morelia boeleni", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Morelia bredli", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Morelia spilota", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Morelia viridis", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python anchietae", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python bivittatus", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python breitensteini", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python brongersmai", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python curtus", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python molurus molurus", min_year = 2009)
#Plot_live_imports(data = vkmCites::Pythons, Species = "Python  molurus", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python regius", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python reticulatus", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python sebae", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python timoriensis", min_year = 2009)
Plot_imports(data = vkmCites::Pythons, Species = "Python  molurus", min_year = 2009)
```

Added figure title
```{r}
Plot_imports_tc(data = vkmCites::Pythons, Species = "Apodora papuana", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Aspidites melanocephalus", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Liasis mackloti", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Morelia boeleni", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Morelia bredli", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Morelia spilota", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Morelia viridis", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python anchietae", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python bivittatus", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python breitensteini", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python brongersmai", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python curtus", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python molurus molurus", min_year = 2009)
#Plot_live_imports(data = vkmCites::Pythons, Species = "Python  molurus", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python regius", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python reticulatus", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python sebae", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python timoriensis", min_year = 2009)
Plot_imports_tc(data = vkmCites::Pythons, Species = "Python  molurus", min_year = 2009)
```

